Short-term synaptic and neuronal plasticity act in synergy for deviance detection in spiking networks

### 2022-12-12 paper-1/manuscript.tex
Include CI level in boxplot caption

\begin{figure*}%
    \centering
    \includegraphics{fig2.pdf}
    \caption{}
    \label{fig2}
\end{figure*}
\textbf{Fig. 2} Deviance detection in vitro and in silico. \textbf{a} Response of a 2 \times 4~mm neuronal cell culture on a multi-electrode array, adapted from \cite{Kubota2021-dx}. Curves represent the average number of spikes per electrode in each 10~ms bin in response to target stimulation in the indicated sequence. Unlike in our study, oddball sequences here were split 10\%/90\%, and 10 equally frequent stimuli were used for the msc sequence. \textbf{b} Sample model response, showing average network-wide spike counts after stimulation with target (A) in the indicated sequence (same color code as panel \textbf{a}). Both in vitro and in the model, the dev response is very large, followed by an intermediate msc response and a low std response. \textbf{c} Mismatch, SSA and deviance detection indices (see Equation \ref{eqn-ddi}) across networks and stimuli (n = 120). In this and later boxplots, the median is indicated with an orange line, notches indicate the confidence interval for the median calculated by bootstrap with 10000 iterations, boxes indicate the inter-quartile range (IQR), whiskers extend to 1.5 times the IQR or to the data extrema, whichever is less, and fliers indicate individual data points beyond the whisker end points

>>>>

\begin{figure*}%
    \centering
    \includegraphics{fig2.pdf}
    \caption{}
    \label{fig2}
\end{figure*}
\textbf{Fig. 2} Deviance detection in vitro and in silico. \textbf{a} Response of a 2 \times 4~mm neuronal cell culture on a multi-electrode array, adapted from \cite{Kubota2021-dx}. Curves represent the average number of spikes per electrode in each 10~ms bin in response to target stimulation in the indicated sequence. Unlike in our study, oddball sequences here were split 10\%/90\%, and 10 equally frequent stimuli were used for the msc sequence. \textbf{b} Sample model response, showing average network-wide spike counts after stimulation with target (A) in the indicated sequence (same color code as panel \textbf{a}). Both in vitro and in the model, the dev response is very large, followed by an intermediate msc response and a low std response. \textbf{c} Mismatch, SSA and deviance detection indices (see Equation \ref{eqn-ddi}) across networks and stimuli (n = 120). In this and later boxplots, the median is indicated with an orange line, notches indicate the 95\% confidence interval for the median calculated by bootstrap with 10000 iterations, boxes indicate the inter-quartile range (IQR), whiskers extend to 1.5 times the IQR or to the data extrema, whichever is less, and fliers indicate individual data points beyond the whisker end points
